\ttitle

### 2013-11-21 Chapters/Chapter3/one_class_classification.tex
Add intro in chapter on OCC

% !TEX root = ../../main.tex
\section{One-Class Classification}\label{sec:one_class_classification}

\TODO{bridge that explains why \gls{occ} is interesting, relating it to outlier/change detection}

>>>>

% !TEX root = ../../main.tex
\section{One-Class Classification}\label{sec:one_class_classification}
As discussed in the previous section, change detection in time series can be implemented using outlier, or novelty, detection.
To regard a data point as an outlier, there must be a model of the normal time series data and a (dis)similiarity measure defined over the model and data objects.
When a data point differs enough from the created model, it can be labeled as an outlier.
The class of \gls{occ} algorithms is especially designed for that purpose.
The algorithms build up a model of the data, assuming only normal data objects are available (or a very limited amount of example outlier data objects).
This differs from classical classification algorithms, which commonly rely of both positive and negative examples.

In \Cref{subsec:occ-problem-formulation} the problem formulation of \gls{occ} methods is explained.
In \cref{subsec:occ-methods} an overview of \gls{occ} methods is given.
The following section will discuss one specific set of methods, the \gls{oc-svm} which use \glspl{svm} to model the normal training data.
